### 2025-05-21 basic-statistics.qmd
20250414 - add packages and DOIs
20250520 - update package list

```{r}
library("petersenlab")
library("DescTools")
library("pwr")
library("pwrss")
library("WebPower")
library("grid")
library("tidyverse")
```

@@

You can use the following interactive graph to visualize various distributions according to a specified [center](#sec-descriptiveStatisticsCenter) (mean), [spread](#sec-descriptiveStatisticsSpread) (standard deviation), and [shape](#sec-descriptiveStatisticsShape) (skewness and kurtosis).
Try varying the standard deviation, skewness, and kurtosis to see the impact of each.

>>>>

```{r}
library("petersenlab")
library("DescTools")
library("pwr")
library("pwrss")
library("WebPower")
library("grid")
library("psych")
library("tidyverse")
```

@@

You can use the following interactive graph to visualize various distributions according to a specified [center](#sec-descriptiveStatisticsCenter) (mean), [spread](#sec-descriptiveStatisticsSpread) (standard deviation), and [shape](#sec-descriptiveStatisticsShape) (skewness and kurtosis).
Try varying the standard deviation, skewness, and kurtosis to see the impact of each.
The interactive graph was created using the `shiny` [@R-shiny] and `PearsonDS` [@R-PearsonDS] packages.
The source code for interactive graph is here: <https://github.com/isaactpetersen/DistributionVisualizer>.

### 2025-05-21 getting-started.qmd
20250409 - working directory
20250520 - update package list

1. Install `R`: <https://cran.r-project.org>
1. Install `RStudio Desktop`: <https://posit.co/download/rstudio-desktop>
1. After installing `RStudio`, open `RStudio` and run the following code in the console to install several key `R` packages:
   ```{r}
   #| eval: false

   install.packages(
     c("petersenlab","remotes","nflreadr","nflfastR","nfl4th","nflplotR",
     "gsisdecoder","progressr","lubridate","tidyverse","psych"))
   ```
1. Some necessary packages, including the [`ffanalytics` package](https://github.com/FantasyFootballAnalytics/ffanalytics) [@R-ffanalytics], are hosted in GitHub and need to be installed using the following code (after installing the `remotes` package [@R-remotes] above):
   ```{r}
   #| eval: false

   remotes::install_github("FantasyFootballAnalytics/ffanalytics")
   ```

@@

@@

Here is how you save a `.RData` file using a *relative path*:

>>>>

1. Install `R`: <https://cran.r-project.org>
1. Install `RStudio Desktop`: <https://posit.co/download/rstudio-desktop>
1. After installing `RStudio`, open `RStudio` and run the following code in the console to install the `R` packages used in this book (note: this will take a while):
   ```{r}
   #| eval: false

   install.packages(
     c("petersenlab","remotes","knitr","rmarkdown","dplyr",
       "ggplot2","tidyverse","psych","xfun","downlit","xml2",
       "nflreadr","nflplotR","nflfastR","nflseedR","nfl4th",
       "gsisdecoder","progressr","DescTools","pwr","pwrss",
       "WebPower","XICOR","dagitty","ggdag","lubridate",
       "ggtext","gghighlight","ggExtra","grid","patchwork",
       "pROC","lme4","lmerTest","MuMIn","emmeans","pbkrtest",
       "sjstats","AICcmodavg","rstan","brms","bbmle",
       "fitdistrplus","mclust","magrittr","viridis","viridisLite",
       "msir","plotly","webshot2","quantmod","fPortfolio",
       "xts","zoo","forecast","stringi","parallel","parallelly",
       "doParallel","missRanger","powerjoin","caret","gpboost",
       "ggridges","corrplot","rms","car","caret","performance",
       "correlation","interactions","lavaan","mice","miceadds",
       "robustbase","see"))
   ```
1. Some necessary packages, including the [`ffanalytics` package](https://github.com/FantasyFootballAnalytics/ffanalytics) [@R-ffanalytics], are hosted in GitHub (and are not hosted on the Comprehensive R Archive Network [CRAN]) and thus need to be installed using the following code (after installing the `remotes` package [@R-remotes] above)[^petersenlabPackageGitHub]:
   ```{r}
   #| eval: false

   remotes::install_github("DevPsyLab/petersenlab")
   remotes::install_github("FantasyFootballAnalytics/ffanalytics")
   remotes::install_github("stan-dev/cmdstanr")
   ```

[^petersenlabPackageGitHub]: Although the [`petersenlab`](https://cran.r-project.org/web/packages/petersenlab/index.html) package [@R-petersenlab] is hosted on CRAN, installing from GitHub will ensure you have the latest version.

@@

To determine where you working directory is, you can type:

```{r}
getwd()
```

To change your working directory, you can type:

setwd("C:/Users/myusername/")
```

@@

Here is how you save a `.RData` file using a *relative path* (i.e., relative to your working directory):
